\Section{Introduction}
\label{sec:introduction}

The discovery of the Higgs boson by the CMS and ATLAS experiments at the Large Hadron Collider in 2012 has opened frontiers towards new physical phenomena \cite{Chatrchyan_2012}. As the Standard Model of Particle Physics (SM) is incomplete, precision measurements in the Higgs sector are promising candidates for Beyond the Standard Model model-limiting measurements. It has been proposed that the ratio of cross sections of the gluon fusion induced ZH final states to the quark induced ZH production is a sensitive observable towards such phenomena \cite{Harlander_2018}. As the direct extraction of the gluon fusion induced process is limited by current experimental setup and analysis techniques due to the destructive interference of the contributing diagrams, the quark induced WH production cross section is included in the proposed measurement.

Newly developed deep learning methods have shown great success in analytically unsolvable tasks such as image classification, generation and captioning, text translation, -generation and regression tasks \cite{LeCun2015}. In a particle physics context, they have become a powerful tool for jet-flavour identification, pileup mitigation, detector effect simulation and process classification \cite{Schwartz_2021}. Most of these modern approaches are built upon neural networks and tackle the challenge of posterior inference by data-driven methods.

Conditional invertible neural networks have already proven to be successful in guided image generation and -colorization \cite{cINN_im_gen} and stochastic model learning \cite{BayesFlow}. Thanks to their invertible nature, these networks can infer the posterior distributions of the underlying model parameters directly. In physics, these networks have proven to be successful in their application to stellar parameter estimation \cite{Ksoll_2020}, cosmic ray source property inference \cite{Bister_2022} and detector effect simulation \cite{Bellagente_2020}.

The continuous growth in model complexity in high energy physics demands increasingly time-consuming likelihood fits. In this thesis inference of signal strength modifiers and nuisance parameters with cINNs will be discussed. Upon successful training, these networks can infer the physics parameters quickly and for low computational cost. The performance measures of the resulting network will be characterized and discussed in detail.

This thesis is structured as follows: ch. \ref{ch:theory} describes the Standard Model and the signal processes for which the signal strength parameters will be inferred. Ch. \ref{ch:experiment} discusses the experimental setup. In ch. \ref{ch:deeplearning}, the foundations of deep learning and conditional invertible neural networks are introduced with a focus on the resulting network setup. Ch. \ref{ch:analysis_strategy} describes the analysis strategy and -setup. The cINN models are described in ch. \ref{ch:network_setup}. Last, the predictions and the performance measures are discussed in \ref{ch:inference}.